### 2015-08-11 paper/manuscript/plos_template.tex
add definition of Frobenius distance

@@

To provide a more comprehensive practical illustration of
our method, we applied it to somatic mutation data from 30 cancer types \cite{pmid23945592}.
We applied the method to each cancer type separately to assess similarity of estimated signatures across cancer types.
For each cancer type we selected the number of signatures $K$ by fitting the model with increasing $K$ and examining the log-likelihood, bootstrap errors, and correlation of membership parameters.
The selected values of $K$ are given in S2 Table.
Also, we simply removed somatic mutations located in an intergenic region to include transcription strand biases as mutation features.
Finally, we merged similar mutation signatures across different cancer types 
(when their Frobenius Distance were $<$ $0.6$). 
% XXX WHAT KIND OF CLUSTERING?
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).

>>>>

\DeclareMathOperator{\Tr}{Tr}

@@

To provide a more comprehensive practical illustration of
our method, we applied it to somatic mutation data from 30 cancer types \cite{pmid23945592}.
We applied the method to each cancer type separately to assess similarity of estimated signatures across cancer types.
For each cancer type we selected the number of signatures $K$ by fitting the model with increasing $K$ and examining the log-likelihood, bootstrap errors, and correlation of membership parameters.
The selected values of $K$ are given in S2 Table.
Also, we simply removed somatic mutations located in an intergenic region to include transcription strand biases as mutation features.
Finally, we merged similar mutation signatures across different cancer types 
(when their Frobenius Distance were $<$ $0.6$, where Frobenius Distance between two matrices ($\bm{F}_1$, $\bm{F}_2$) is $\sqrt{ \Tr  (\bm{F}_1 -  \bm{F}_2 )  (\bm{F}_1 -  \bm{F}_2 )^t }$).
% XXX WHAT KIND OF CLUSTERING?
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).
